Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-06-13 article.rnw
Change the lines in the histogram to be more colourblind-friendly.
Green and purple instead of green and red.

\begin{figure}
	\centering
	\begin{subfigure}{0.65\textwidth}
	<<>>=
		hist(brute_data$statistics[[ic]],
			main="",
			xlab=ic_name,
			xaxs='i',
			yaxs='i',
			ylim=c(0,6000)
		)
		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="red")
	@
	\end{subfigure}

	\caption{%
		Histogram of the {\ic} values of Lotka--Volterra model fits with all possible groupings of interaction coefficients.
		The dashed green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model in which all competition coefficients are fitted independently.
		The dotted red line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
	}
	\label{fig:ic}
\end{figure}
% DBS: Reconsider green and red to be more colour-blind friendly. I've already changed it so that the lines are different types.

>>>>

\begin{figure}
	\centering
	\begin{subfigure}{0.65\textwidth}
	<<>>=
		hist(brute_data$statistics[[ic]],
			main="",
			xlab=ic_name,
			xaxs='i',
			yaxs='i',
			ylim=c(0,6000)
		)
		abline(v = brute_data$fully_separated_statistics[[ic]], lwd=2, lty="dashed", col="green")
		abline(v = brute_data$fully_grouped_statistics[[ic]], lwd=2, lty="dotted", col="purple")
	@
	\end{subfigure}

	\caption{%
		Histogram of the {\ic} values of Lotka--Volterra model fits with all possible groupings of interaction coefficients.
		The dashed green line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model in which all competition coefficients are fitted independently.
		The dotted purple line shows the {\ic} value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model in which every pair of species shares a single interaction coefficient.
	}
	\label{fig:ic}
\end{figure}
